\documentclass[10pt]{article}

% Tenure-facing CV redraft for Olga Gasparyan
% Strategy: foreground disciplinary political science and methodology work,
% then present Lancet work as peer-reviewed collaborative reports with concise contribution notes.

\usepackage[letterpaper,margin=0.72in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{enumitem}
\usepackage{tabularx}
\usepackage{array}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{lastpage}
\usepackage{fancyhdr}

\hypersetup{
    colorlinks=true,
    linkcolor=black,
    urlcolor=blue!45!black
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\setlist[itemize]{leftmargin=1.15em,itemsep=1.5pt,topsep=2pt,parsep=0pt}
\setlist[enumerate]{leftmargin=1.6em,itemsep=2.5pt,topsep=2pt,parsep=0pt}

\titleformat{\section}{\large\bfseries\scshape}{}{0pt}{}[\titlerule]
\titlespacing*{\section}{0pt}{9pt}{4pt}
\titleformat{\subsection}{\normalsize\bfseries}{}{0pt}{}
\titlespacing*{\subsection}{0pt}{5pt}{1.5pt}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\cfoot{\small Olga Gasparyan -- CV -- Page \thepage\ of \pageref{LastPage}}

\newcommand{\me}{\textbf{Gasparyan, Olga}}
\newcommand{\cvitem}[2]{\textbf{#1}\hfill #2\\}
\newcommand{\entry}[2]{\textbf{#1}\hfill #2\\}
\newcommand{\note}[1]{\emph{#1}}
\newcommand{\status}[1]{ {\small\textit{[#1]}}}

\begin{document}

{\LARGE \textbf{Olga Gasparyan}}\\[3pt]
Department of Political Science, Florida State University\\
569 Bellamy Building, Tallahassee, FL 32304\\
\href{mailto:ogasparyan@fsu.edu}{ogasparyan@fsu.edu} \; | \; \href{http://www.olgasparyan.com}{www.olgasparyan.com}\\[-2pt]
\vspace{2pt}
{\small Last updated: July 2026}

\section{Academic Appointments}
\entry{Florida State University, Department of Political Science}{2023--present}
Assistant Professor

\entry{Hertie School, Data Science Lab, Berlin}{2021--2023}
Postdoctoral Associate

\entry{SCRIPTS Cluster of Excellence, Data and Methodology Center}{2021--2022}
Postdoctoral Associate and Academic Coordinator

\section{Education}
\entry{University of Rochester}{2020}
Ph.D., Political Science\\
Fields: Comparative Politics, Political Methodology\\
Committee: Randall Stone (chair), Alexander Lee, Anderson Frey, Gretchen Helmke

\entry{University of Rochester}{2018}
M.A., Political Science

\entry{National Research University Higher School of Economics, Moscow}{2014}
M.A., Political Science, with honors

\entry{National Research University Higher School of Economics, Moscow}{2012}
B.A., Political Science, with honors

\section{Research Areas}
Visual politics and political communication; political methodology; computational social science; comparative public policy; governance and public goods provision.

\section{Peer-Reviewed Publications}

\subsection{Political Science and Methodology}
\begin{enumerate}
    \item \me\ and Elena Sirotkina. 2025. ``Media Choice and Audience Perceptions: Evidence from Visual Framing of Immigration in News Stories.'' \textit{PLOS One} 20(9): e0331219. \note{Equal-author collaboration; first paper in the visual politics research agenda.}

    \item \me. 2024. ``Indirect Rule and Public Goods Provision: Evidence from Colonial India.'' \textit{Political Science Research and Methods} 12(2): 444--450.

    \item Crisman-Cox, Casey, \me, and Curtis Signorino. 2023. ``Finding and Accounting for Separation Bias in Strategic Choice Models.'' \textit{Political Analysis} 31(3): 414--429.
\end{enumerate}

\subsection{Climate, Health, and Public Discourse}
\begin{enumerate}[resume]
    \item Kriit, Heidi, \ldots, \me\ et al. 2026. ``The 2026 Europe Report of the Lancet Countdown on Health and Climate Change: Narrowing Window for Decisive Health Action.'' \textit{The Lancet Public Health} 11(6): e386--e407.

    \item Romanello, Marina, \ldots, \me\ et al. 2025. ``The 2025 Report of the Lancet Countdown on Health and Climate Change.'' \textit{The Lancet} 406(10521): 2804--2857. \note{Lead contributor, Indicator 5.4.2: methodology, data analysis, and results writing on engagement by international organizations.}

    \item Romanello, Marina, \ldots, \me\ et al. 2024. ``The 2024 Report of the Lancet Countdown on Health and Climate Change: Facing Record-Breaking Threats from Delayed Action.'' \textit{The Lancet} 404(10465): 1847--1896. \note{Contributor, Indicator 5.4.2: methodology, data analysis, and results writing on engagement by international organizations.}

    \item van Daalen, Kim R., \ldots, \me\ et al. 2024. ``The 2024 Europe Report of the Lancet Countdown on Health and Climate Change: Unprecedented Warming Demands Unprecedented Action.'' \textit{The Lancet Public Health} 9(7): e495--e522. \note{Indicator contributor: constructed indicators on media coverage and public rhetoric about climate change and health co-benefits; led data collection and computational analysis for individual engagement indicator.}

    \item Romanello, Marina, Claudia di Napoli, \ldots, \me\ et al. 2023. ``The 2023 Report of the Lancet Countdown on Health and Climate Change: The Imperative for a Health-Centred Response in a World Facing Irreversible Harms.'' \textit{The Lancet} 402(10419): 2346--2394.

    \item van Daalen, Kim R., Marina Romanello, Joacim Rocklov, \ldots, \me\ et al. 2022. ``The 2022 Europe Report of the Lancet Countdown on Health and Climate Change: Towards a Climate Resilient Future.'' \textit{The Lancet Public Health} 7(11): e942--e965.
\end{enumerate}

\section{Manuscripts Under Review}
\begin{enumerate}
    \item Tertytchnaya, Katerina, Quintin Beazer, Holger L. Kern, Eugenia Nazrullaeva, Ksenia Northmore-Ball, and \me. ``Public Support for Patriotic Education under Authoritarianism: Evidence from Russia.'' \status{Revise and resubmit, \textit{Journal of Experimental Political Science}}
\end{enumerate}

\section{Working Papers and Works in Progress}

\subsection{Visual Political Communication and Political Methodology}
\begin{enumerate}
    \item \me\ and Elena Sirotkina. ``From Pixels to Perspectives: Audience-Specific Visual Sentiment in Political Imagery'' 

    \item Sirotkina, Elena, and \me. ``Vision and Division: Partisan Identity and Visual Processing of Political Imagery'' 

    % \item \me\ and Elena Sirotkina. ``Focused Vision: How Patterns of Looking Influence Political Attitudes.'' \status{Registered-report project in preparation}

    \item \me. ``Visual Stimuli as Multi-Level Treatments: Estimation and Causal Interpretation in Conjoint Experiments''
\end{enumerate}

\subsection{Comparative Public Policy}
\begin{enumerate}
    \item \me. ``Local Elections, Efficiency, and Resource Allocation: Evidence from Russian Cities''

    \item Dasandi, Niheer, \me, Slava Jankin, and Neil Mitchell. ``The Use and Abuse of Human Rights Language: Evidence from the UN General Debate, 1946--2022''

    \item Gross, Greta, \me, Slava Jankin, and Mark Hallerberg. ``Attributing Blame in Times of Austerity: A Cross-National Computational Study of Finance Ministers' Budget Speeches.''
\end{enumerate}

\section{Other Publications}
\begin{enumerate}
    \item \me. 2019. ``The Importance and Peculiarities of Archival Work in Political Science.'' \textit{Comparative Politics Newsletter} 29(2): 5--11.
\end{enumerate}

\section{Grants, Fellowships, and Awards}

\subsection{External and Collaborative Grants}
\begin{itemize}
    % \item Russell Sage Foundation Research Grant, application submitted, 2025 (\$200,000 requested).
    \item Horizon Europe, Climate Action To Advance Healthy Societies in Europe (CATALYSE), Working Group on innovative health surveillance and forecasting tools, 2022. Co-Investigator. Total funding requested: EUR 10,354,000; Hertie component: EUR 975,000.
    \item SCRIPTS Small Grants, ``The Not-So-Universal Declarations: Types and Effects of Human Rights Rhetoric in the UN General Assembly,'' 2022. Co-Investigator. EUR 40,000.
\end{itemize}

\subsection{Internal Grants, Fellowships, and Awards}
\begin{itemize}
    \item First Year Assistant Professorship Grant, Florida State University, Summer 2024. \$20,000.
    \item COSSPP Individual Faculty Research Program, Florida State University, Summer 2024. \$10,000.
    \item Hertie School Faculty Activity Fund, AY 2021--2022. EUR 14,550.
    \item Dean's Post-Field Research Dissertation Completion Fellowship, University of Rochester, 2020--2021 (declined). \$20,000.
    \item Carnegie/Harriman Research Grant, Columbia University, 2020. \$16,000.
    \item Beck Research Grant, University of Rochester, 2019 (declined).
    \item The Harriman Institute, Columbia University, Travel Grant, 2019. \$2,250.
    \item Watson Field Work Grant, University of Rochester, 2019. \$1,600.
    \item Summer Seed Field Work Grant, University of Rochester, 2018. \$3,000.
    \item Second Year Paper Lanni Fellowship, University of Rochester, 2017. \$1,100.
    \item PEPR Research Grant, University of Rochester, 2016. \$1,100.
    \item Oxford Russian Fund Fellowship, Higher School of Economics, 2010--2012.
    \item Best Lecturer at Political Science Department Award, Higher School of Economics, 2013--2014.
    \item Golden HSE Award, ``Silver Nestling,'' Higher School of Economics, 2012.
\end{itemize}

\section{Invited Talks and Conference Presentations}
\textbf{Selected invited talks and workshops.} University of Southern California PEDev Mini-Conference (2025); University of Houston, Information and Messages in Sociopolitical Life (2025); VIM, Washington University in St. Louis (2024); University of Bremen Economic Colloquium (2022); PolMeth-Europe, Hamburg (2022); Connected Politics Lab Seminar Series, University College Dublin (2022); Women in Political Methodology Speaker Series (2021); Wisconsin Russia Project Young Scholars Conference (2021); Joint Harriman Institute and Jordan Center Graduate Student Research Workshop (2019); Summer Workshop in Russian Economic History and Historical Political Economy, University of Wisconsin--Madison (2019).\\[3pt]
\textbf{Conference presentations.} APSA (2018--2020, 2022--2024, 2026); PolMeth (2022, 2026); MPSA (2014--2015, 2018--2022, 2024); EPSA (2021--2022, 2025); SPSA (2025); IPSA (2025); ISA (2022); ASEEES (2021).

\section{Teaching}

\subsection{Florida State University}
\begin{itemize}
    \item POS 5737: Probability and Statistics, graduate methods sequence. Fall 2023, Fall 2024, Fall 2025, Fall 2026
    \item PUP 3002: Introduction to Public Policy, undergraduate. Fall 2023, Spring 2024, Fall 2024, Spring 2025, Fall 2025, Spring 2026, Fall 2026
    \item PUP 5015: Comparative Public Policy, graduate seminar. Spring 2025.
\end{itemize}

% \subsection{New Course Preparations}
% \begin{itemize}
%     \item PUP 3002: Introduction to Public Policy, in-person version, Fall 2025.
%     \item PUP 5015: Comparative Public Policy, graduate seminar, Spring 2025.
% \end{itemize}

\section{Mentorship}
\subsection{Graduate Mentorship}
\begin{itemize}
    \item Jessica Jatau, first-year paper advisor, 2025--2026.
    \item David Akindoyin, first-year paper advisor, 2024--2025.
    \item Huijie Xu, first-year paper advisor, 2023--2024.
\end{itemize}

\subsection{Undergraduate Mentorship}
\begin{itemize}
    \item Francisca Puiatti, honors thesis committee member.
\end{itemize}

\section{Service}

\subsection{Departmental and University Service}
\begin{itemize}
    \item Comparative Politics Workshop Coordinator, Florida State University, 2023--present.
    \item Public Policy Search Committee, Department of Political Science, Florida State University, 2023--2024; 2025--2026.
    \item Executive Committee, Department of Political Science, Florida State University, 2024--2025.
    \item Undergraduate Studies Committee, Department of Political Science, Florida State University, 2023--present.
    \item Southern Workshop in Empirical Political Science, organizing team, Florida State University, 2026.
\end{itemize}

\subsection{Prior Institutional Service}
\begin{itemize}
    \item Research Ethics Committee, Hertie School, 2022--2023.
    \item Organizer and Coordinator, Hertie Data Science Summer School, 2021, 2022.
    \item Hertie School Coordinator, CIVICA Data Science Seminar Series, 2021--2023.
    \item Coordinator, Women's Working Group, University of Rochester Political Science Department, 2018--2019.
    \item Graduate Assistant, University of Rochester Internships in Europe Programme, 2017.
\end{itemize}

\subsection{Professional Service}
\begin{itemize}
    \item Reviewer: \textit{International Journal of Communication, European Journal of Political Research, Political Analysis, Political Behavior}.
\end{itemize}

\section{Professional Memberships}
APSA, MPSA, EPSA, SPSA, PolMeth, ASEEES, ISA.

\section{Languages and Technical Skills}
\begin{tabularx}{\textwidth}{@{}>{\bfseries}l X@{}}
Languages & Russian (native), English, Spanish, German, Korean (beginner).\\
Software & R, Python, Stata, SQL, ArcGIS, QGIS, \LaTeX, HTML5/CSS, JavaScript (basic).\\
Methods & Causal inference,  machine learning, deep learning for image analysis, computational text analysis, survey and experimental design,  eye-tracking methods, geospatial analysis.\\
\end{tabularx}

\end{document}
